---
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options: 
  chunk_output_type: console
output: rmarkdown::html_vignette
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(glue)
library(viridis) 
library(kableExtra)
library(lubridate)
library(googlesheets4)


# Using this guide https://www.obrien.page/blog/2023/03_10_google_and_github_actions/

googlesheets4::gs4_auth(path = Sys.getenv('GDRIVE_PAT')) # google-sheets-github@astral-web-375220.iam.gserviceaccount.com
dat <- read_sheet("1h3a1H4UwZHDUUj_s6MWUVDrhn_qqlCm6PTM8lsaHMWA", col_type="cccccDcDcnnnnnnnccccccccccccccc")

# remove everything without a name
dat <- dat[is.na(dat$Name)==F,]
# Remove the year row
dat <- dat[!(dat$Name %in% c(2025,2026,2027)),]

# Get todays date
t <- Sys.Date()

# Create a list of confirmed/arrived reservations with start and end dates.
dat_complete <- dat[is.na(dat$`Arrival Date`)==F & is.na(dat$`Departure Date`)==F,]
# Subset to rows with booking numbers
dat_complete <- dat_complete[is.na(dat_complete$`# people [adults]`)==F,]
# Subset to just confirmed
dat_confirmed <- dat_complete[dat_complete$`Booking status` %in% c("Arrived", "Confirmed", "Confirmed_100", "Confirmed_50" ),]
```

```{r loop1, include=FALSE}
# For each booking, create a list of the number of people and the dates active
daily_guests <- list()
#i <- 2

for(i in 1:nrow(dat_confirmed))
{
  tmp <- dat_confirmed[i,]
  if(tmp$`Arrival Date`==tmp$`Departure Date`)
  {
    daily_guests[[i]] <- data.frame(Name=tmp$Name, Last_Name = tmp$`Last Name`,Date=tmp$`Arrival Date`[1],
                                      Adults=tmp$`# people [adults]`[1],Children= tmp$`# people [kids u12]`[1])     
  } else {
  daily_guests[[i]] <- data.frame(Name=tmp$Name,Last_Name = tmp$`Last Name`, Date=seq(tmp$`Arrival Date`, tmp$`Departure Date`, by=1 ),
             Adults=tmp$`# people [adults]`[1],Children= tmp$`# people [kids u12]`[1]) 
  }
}

daily_guests <- bind_rows(daily_guests)


# Today
tmp <- daily_guests[daily_guests$Date==t,]

```

**Today's visitor count** The number of people currently listed as "confirmed" for today's date are: **`r sum(tmp$Adults) + sum(tmp$Children)`** - (`r sum(tmp$Adults)` adults and `r sum(tmp$Children)` children).

The table this was calculated from (will delete if it looks correct):

```{r, echo=F}
tmp %>%
  kbl(row.names = FALSE) %>%
  kable_styling() %>% 
  column_spec (1:3,border_left = T, border_right = T) 
```

**Count for the next 7 days**

```{r, echo=F, include=F}
tmp <- daily_guests[daily_guests$Date>=t & daily_guests$Date<=(t+7) ,]
tmp <- tmp %>% group_by(Date) %>% summarise(Adults=sum(Adults), Children=sum(Children))
tmp$Day <- weekdays(tmp$Date)
tmp <- tmp[,c("Date", "Day", "Adults", "Children")]
tmp$Total <- tmp$Adults+tmp$Children
```

```{r, echo=F}
tmp %>%
  kbl(row.names = FALSE) %>%
  kable_styling() %>% 
  column_spec (1:3,border_left = T, border_right = T) 
```


**Arrivals in the next 7 days** The following list shows the groups which should be arriving (confirmed and provisional):

```{r  c05, echo=F}
tmp <- dat[dat$`Arrival Date`> t & dat$`Arrival Date`<=(t+7) & is.na(dat$`Arrival Date`)==F & dat$`Booking status`!="Cancelled",]
tmp <- tmp[, c("Name", "Last Name", "Visitor Type", "Booking status", "Arrival Date", "# Nights", "# people [adults]", "# people [kids u12]")]

```

```{r, echo=F}
tmp %>%
  kbl(row.names = FALSE) %>%
  kable_styling() %>% 
  column_spec (1:3,border_left = T, border_right = T) 
```


**Departures in the next 7 days** The following list shows the groups which should be leaving (confirmed and provisional):

```{r  c05a, echo=F}
 
tmp <- dat[dat$`Arrival Date`> t & dat$`Arrival Date`<=(t+7) & is.na(dat$`Arrival Date`)==F & dat$`Booking status`!="Cancelled",]
tmp <- tmp[, c("Name", "Last Name", "Visitor Type", "Booking status", "Arrival Date", "# Nights", "# people [adults]", "# people [kids u12]")]

```

```{r, echo=F}
tmp %>%
  kbl(row.names = FALSE) %>%
  kable_styling() %>% 
  column_spec (1:3,border_left = T, border_right = T) 
```


